Thermodynamic fragments for magic states in quantum computation

### 2021-03-07 magic_paper.tex
Started discussion on rate comparison

It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve and defined as
\begin{equation}
	\widetilde{w}(\rho|\sigma)_i \coloneqq \frac{w(\rho)_i}{w(\sigma)_i},
\end{equation}
is called the Gibbs-rescaled distribution of $\rho$ with respect to $\sigma$.

@@

In the sections~\cref{sec:unital,sec:stab}, we study majorization constraints on magic distillation arising in different fragments. 
For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
\begin{equation}\label{eq:noisysn}
    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
\end{equation}
in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange} and the induced noise is uniform. 
For $\epsilon=0$, this state is a qutrit of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.

@@

These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabilizer state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind. 
Without loss of generality, we can always write a stabiler state $\sigma$ as a Gibbs state $\sigma = \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.

We focus on the distillation process
\begin{equation}\label{eq:stdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
\end{equation}
where the noisy Strange state is given in~\cref{eq:noisysn}, but more general states can be handled in exactly the same manner.
Notice that tensoring in copies of $\gamma_\beta$ does not affect the process, since the state is free.
In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$. 
Finally, we assume a \nick{generous} range of initial noise levels, $\epsilon \leq 3/7$, so that the largest Wigner component of the 1-copy noisy magic state is negative.

\nick{Specify: How general can the states get? What about not full-rank states? Should we include the case of odd $n$ or non-zero $\epsilon'$ in the appendix? What about $\epsilon>0$?}

@@

>>>>

It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.
The vector of ratios $\widetilde{\bmw}(\rho|\sigma)$ used to construct the curve is defined as
\begin{equation}
	\widetilde{w}(\rho|\sigma)_i \coloneqq \frac{w(\rho)_i}{w(\sigma)_i},
\end{equation}
is called the Gibbs-rescaled distribution of $\rho$ with respect to $\sigma$.

@@

In the sections~\cref{sec:unital,sec:stab}, we study majorization constraints on magic distillation arising in different fragments. 
For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
\begin{equation}\label{eq:noisysn}
    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
\end{equation}
in $\O_\sigma$, where $\ket{\rm{S}}$ is defined in~\cref{fig:strange} and the induced noise is uniform.

For $\epsilon=0$, this state is a qutrit of maximal sum-negativity / mana~\cite{cit:veitch2} and therefore acts as the ideal distiallation target, analogous to a Bell state in bipartite entangelement theory.
The Strange state is exceptionally symmetric under Clifford transformations and as a result there exists a \emph{twirling} protocol, discussed in detail in~\cite{cit:prakash,cit:prakash2}, allowing for the conversion of any noisy magic state to the form of~\cref{eq:noisysn} via Cliffords.

@@

These bounds can be interpreted in two different ways: on one hand they can be viewed as a family of upper bounds parameterized by a stabilizer state $\sigma$, on the other we can associate $\sigma$ to actual hardware limitations or to biased noise models in which it is an equilibrium state of some kind. 
Without loss of generality, we can always write a stabiler state $\sigma$ as a Gibbs state $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ as discussed in~\cref{sec:major_frag}.

We focus on the distillation process
\begin{equation}\label{eq:stdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
\end{equation}
where the noisy Strange state is given in~\cref{eq:noisysn}, but more general states can be handled in exactly the same manner.
We also highlight that any magic state can be written in terms of a noisy Strange state.
Notice that tensoring in copies of $\gamma_\beta$ does not affect the process, since the state is free.
In the following result, all copies $n, n', n - n'$ are even with $n > n'$, and $\epsilon'=0$, but the bounds are easily generalised to odd numbers of copies and $\epsilon'$ such that $0 < \epsilon' < \epsilon$. 
Finally, we assume a \nick{generous} range of initial noise levels, $\epsilon \leq 3/7$, so that the largest Wigner component of the 1-copy noisy magic state is negative.

\nick{Specify: How general can the states get? What about not full-rank states? Should we include the case of odd $n$ or non-zero $\epsilon'$ in the appendix? What about $\epsilon>3/7$?}

@@

\section{Comparison with existing distillation rates}
\label{sec:comparison}

We have derived a \emph{distillation bound} $R(\epsilon, \epsilon', \beta)$ for the process
\begin{equation}\label{eq:stdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes n} \longrightarrow \rho_{\rm{S}}(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
\end{equation}
with even $n, n'$ and $0 \leq \epsilon' < \epsilon \leq 3/7$, where the $n$-copy, $\epsilon$-noisy Strange state is
\begin{equation}\label{eq:test}
    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n}.
\end{equation}

The bound informs us that any distillation protocol in the $\gamma_\beta$-fragment with an $\epsilon$-noisy input and $\epsilon'$-noisy output has a \emph{distillation rate} 
\begin{equation}
	\frac{n'}{n} \leq R(\epsilon, \epsilon', \beta).
\end{equation}

We can rephrase this result, saying that any distillation protocol in the $\gamma_\beta$-fragment with an $n$-copy input and $n'$-copy, $\epsilon'$-noisy desired output, must have input noise level 
\begin{equation}
	\epsilon \leq  E\left(\frac{n'}{n}, \epsilon', \beta \right)
\end{equation}
for some error bound $E$ related to $R$.

An $n$-copy state $\rho^n$ has \emph{error rate} $\epsilon$ iff $\rho$ has an overlap of at least $1-\epsilon$ with magic state $\ket{\rm{S}}$,
\begin{equation}
	\bra{\rm{S}}\rho\ket{\rm{S}} \geq 1-\epsilon.
\end{equation}
The $\epsilon$-noisy Strange state $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ has error rate $\frac{2}{3}\epsilon$.
A general state of $n$ qutrits with error rate $\epsilon$ can be converted to the form $\rho_{\rm{S}}(\epsilon_0)^{\otimes n}$ for some noise level $\epsilon_0$ not necessarily equal to $\epsilon$.

Given an $[[n,n',d]]$ error correcting code, a distillation protocol that achieves the process in~\cref{eq:test} requires
\begin{align}
	\epsilon' &\sim O((n\epsilon)^d) \\
	\frac{n}{n'} &\sim O(\log^\gamma{1/\epsilon'}),\ \gamma = \log_d{\left(\frac{n}{n'}\right)}
\end{align}

In~\cite{Bravyi2012,Hastings2018}, the asymptotic rate $O(\log^\gamma{1/\epsilon'})$ is called the \emph{distillation cost}.
\nick{These inequalities seem to be the other way around.}
